Using Genetic Algorithms to Optimize the Analogue Method for Precipitation Forecasting in the Swiss Alps

### 2015-11-19 Optimization case study - Journal of Hydrology/elsarticle-template.tex
First version of the analogue method description.

\usepackage{multirow}
\usepackage{gensymb}
\usepackage{subcaption}

@@

Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{Horton2016, BenDaoud2015}. However, there are mainly 2 parametrizations that are most often used for precipitation forecasting: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.

@@

The other most know parametrization adds a second level of analogy on moisture variables (Table \ref{table:params_R2}). The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa. \cite{Horton2012a} confirmed that this index is better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently. When adding a second level of analogy, we subsample $N_{2}$ dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When we add a second level of analogy, we keep a higher number of analogues on the first level.

@@

Predictors are generally reanalysis datasets. We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis dataset.

The predictand (which is to be predicted) is in our case the daily precipitation (6~a.m. to 6~a.m. the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008. The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.

>>>>

\usepackage{multirow}
\usepackage{gensymb}
\usepackage{subcaption}
%\usepackage{amsmath}

@@

\subsection{References}
\label{sec:references}

Multiple variations of the methods exist, and most of them will not be detailed hereafter \cite[see][for more comprehensive listings]{Horton2016, BenDaoud2015}. However, there are mainly 2 parametrizations that are most often used for precipitation forecasting and that will be considered as reference: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on moisture variables \citep{Obled2002, Bontron2005, Marty2012}.

@@

The other most know parametrization adds a second level of analogy on moisture variables (method 2Z-2MI, Table \ref{table:params_R2}). The predictor that \citet{Bontron2004} found optimal for the France territory is a moisture index made of the product of the precipitable water with the relative humidity at 850~hPa. \cite{Horton2012a} confirmed that this index is better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently. When adding a second level of analogy, we subsample $N_{2}$ dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When we add a second level of analogy, we keep a higher number of analogues on the first level.

@@

Predictors are generally reanalysis datasets. The NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996} are used here, but it can be any other reanalysis dataset.

The predictand (which is to be predicted) is in here the daily precipitation (6~a.m. to 6~a.m. the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008. The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.

\subsection{Performance assessment}
\label{sec:score}

The most used score to assess an AM performance is the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}. It allows assessing the predicted cumulative distribution functions $F(y)$, for example of the precipitation values $y$ from analogue situations, compared to the observed value $y^{0}$. The better the forecast, the smaller the score. The mean CRPS of a forecast series of length $n$ can be written:

\begin{equation}
\label{eq:CRPS}
CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
\end{equation}
where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise. The mean CRPS is averaged on the calibration, respectively the validation periods, on all days.

This score is now commonly used for the evaluation of continuous variables prediction systems \citep{Casati2008, Marty2010}. To compare the value of the score in regard to a reference, we often consider its skill score value, and use the climatological distribution as the reference. The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:

\begin{equation}
\label{eq:CRPSS}
CRPSS = \frac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\frac{CRPS}{CRPS_{r}}
\end{equation}
where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast (which implies $CRPS_{p}~=~0$).
